### 2015-05-11 fundamentals/impl.tex
updates prelim citation to thesis. closes #78

Given a full definition of supply and demand, the \gls{DRE} may be solved either
optimally using a mathematical program or approximately by a simulation-based
heuristic \cite{gidden_agent-based_2014}. If any trade is denoted as exclusive, e.g., if an
analyst desires an assembly-fidelity model, then either a heuristic must be used
or exchanges must be represented as a \gls{MILP}. If no exclusive trades exist,
a \gls{LP} model may be used. In practice, \glspl{LP} solve much faster than
\glspl{MILP}. However, both capabilities exist in \Cyclus in order to
provide users with the desired level of fidelity.

>>>>

Given a full definition of supply and demand, the \gls{DRE} may be solved either
optimally using a mathematical program or approximately by a simulation-based
heuristic \cite{gidden_agent-based_2015}. If any trade is denoted as exclusive, e.g., if an
analyst desires an assembly-fidelity model, then either a heuristic must be used
or exchanges must be represented as a \gls{MILP}. If no exclusive trades exist,
a \gls{LP} model may be used. In practice, \glspl{LP} solve much faster than
\glspl{MILP}. However, both capabilities exist in \Cyclus in order to
provide users with the desired level of fidelity.
